Reproducible Workflow on a Public Cloud for Computational Fluid Dynamics

### 2019-08-14 tex/MesnardoBarba2019.tex
Add sentences about run on finer grid
* at the end of the paragrah about the history of the force coefficients with a footnote pointing to the Jupyter Notebook,
* at the end of the cost analysis

Fig. \ref{fig:force_coefficients} compares the history of the force coefficients between the two- and three-dimensional configurations.
The force coefficients resulting from the two-dimensional simulation of the snake are higher than those obtained for the snake cylinder; we computed a relative difference of $+37.9\%$ and $+14.4\%$ for the time-averaged drag and lift coefficient, respectively (see Table \ref{tab:force_coefficients}).
Two-dimensional computational simulations of fundamentally three-dimensional flows lead to incorrect estimation of the force coefficients, as is well known\cite{mittal_balachandar_1995}.

@@

For the year $2018$, Microsoft Azure granted our research lab a sponsorship (in terms of cloud credits) to run CFD simulations with our in-house software.
With a ``pay-as-you-go'' subscription, users can immediately see how much it costs to run a scientific application on a public cloud; such information is often hidden to end-users on university-managed clusters.
From May to December, we spent a total of $20,614$ USD to run CFD simulations, including a couple dozens of snake simulations.
(The output of those simulations is now being processed to further analyze the complex flow dynamics generated behind the snake model.)
During that period, we have been charged for data management, networking, storage, bandwidth, and virtual machines (Table \ref{tab:azure_charges}).
More than $99\%$ of the charges incurred were for the usage of virtual machines, mainly instances from the NC-series (Table \ref{tab:nc_series}).
To run PetIBM simulations of the snake model, we used the \texttt{NC24r} virtual machines to get access to NVIDIA K80 GPUs and InfiniBand networking.
For example, the two-dimensional snake run reported in the present article cost $55.4$ USD ($2$ \texttt{NC24r} instances with a hourly price of $3.96$ USD for about $7$ hours).
The three-dimensional computation cost $1077.1$ USD ($2$ \texttt{NC24r} instances for about $136$ hours).
(Note that with 3-year-reserved instances, the two- and three-dimensional snake simulations would have only cost $24.6$ and $478.1$ USD, respectively.)

>>>>

Fig. \ref{fig:force_coefficients} compares the history of the force coefficients between the two- and three-dimensional configurations.
The force coefficients resulting from the two-dimensional simulation of the snake are higher than those obtained for the snake cylinder; we computed a relative difference of $+37.9\%$ and $+14.4\%$ for the time-averaged drag and lift coefficient, respectively (see Table \ref{tab:force_coefficients}).
Two-dimensional computational simulations of fundamentally three-dimensional flows lead to incorrect estimation of the force coefficients, as is well known\cite{mittal_balachandar_1995}.
The grid used for the three-dimensional simulation contains about $46$ million cells and is somewhat coarse for Direct Numerical Simulation (DNS) at Reynolds number $2,000$, but acceptable for our exploratory analysis.
A finer grid would be preferable to capture the flow dynamics in details, but the purpose of this paper is not targeting the physics.
We did however run a simulation on a finer grid (about $233$ million cells) resulting in a relative difference (with respect to the "coarse"-grid simulation) of $+6.5\%$ and $+3\%$ for the time-averaged drag and lift coefficients, respectively.
We decided to continue this work with the coarser grid due to the cost difference (see Section \ref{sec:cost}).
Details about this fine-grid simulation are available as supplementary material on the GitHub repository for this study.\footnote{\url{https://nbviewer.jupyter.org/github/barbagroup/cloud-repro/blob/master/misc/independence/grid.ipynb}}

@@

For the year $2018$, Microsoft Azure granted our research lab a sponsorship (in terms of cloud credits) to run CFD simulations with our in-house software.
With a ``pay-as-you-go'' subscription, users can immediately see how much it costs to run a scientific application on a public cloud; such information is often hidden to end-users on university-managed clusters.
From May to December, we spent a total of $20,614$ USD to run CFD simulations, including a couple dozens of snake simulations.
(The output of those simulations is now being processed to further analyze the complex flow dynamics generated behind the snake model.)
During that period, we have been charged for data management, networking, storage, bandwidth, and virtual machines (Table \ref{tab:azure_charges}).
More than $99\%$ of the charges incurred were for the usage of virtual machines, mainly instances from the NC-series (Table \ref{tab:nc_series}).
To run PetIBM simulations of the snake model, we used the \texttt{NC24r} virtual machines to get access to NVIDIA K80 GPUs and InfiniBand networking.
For example, the two-dimensional snake run reported in the present article cost $55.4$ USD ($2$ \texttt{NC24r} instances with a hourly price of $3.96$ USD for about $7$ hours).
The three-dimensional computation cost $1077.1$ USD ($2$ \texttt{NC24r} instances for about $136$ hours).
(Note that with 3-year-reserved instances, the two- and three-dimensional snake simulations would have only cost $24.6$ and $478.1$ USD, respectively.)
The three-dimensional simulation on the finer grid ($233$ million cells) ran on $6$ \texttt{NC24r} instances and cost about $7965$ USD to compute $100,000$ time steps (cost not included in \ref{tab:azure_charges}).
This is more than $7$ times the cost we paid for the "coarse"-grid run!
It would have been too expensive to run a batch of simulations on the finer grid for our exploratory analysis of the flow around the snake cylinder.
